### 2018-02-08 results.tex
finished figure 9

\begin{figure*}
	\centering
	% \includegraphics[width=\textwidth]{figures/pdf/figure-09}
	\caption{}
	\label{fig:trees}
\end{figure*}

>>>>

\begin{figure*}
	\centering
	\includegraphics[width=0.86\textwidth]{figures/pdf/figure-09}
	\caption{Selected trees \textbf{(a)} T1, \textbf{(b)} T2, and \textbf{(c)} T3. In each case the decision nodes of the trees contain the code corresponding to the metric (see Table \ref{tab:metrics}) used and the branches beneath each node show the limit value to be used to select the next level in the tree. At the bottom, normalized histograms are shown to indicate the distribution of the samples at each leaf-node according to the validation classes with codes P, F, G, and E for poor, fair, good, and excellent, respectively. At the top of each histogram is the total count of samples at the corresponding leaf node. The histograms highlight the dominant validation class. The color version of this figure is available only in the electronic edition.}
	\label{fig:trees}
\end{figure*}
